Analysis for Project

### 2021-11-11 analysis/analysis.Rmd
Panelize figure by group
To keep things a little cleaner,  I redesigned the panelized figure to panelize by each multracial group which allows readers to much more easily see where the multiracial group falls relative to the monoracial constituent groups. This new function only takes one model. I think trying to compare models in the same figure would be too difficult, so think about other ways of showing change across controls.

```{r}
plot_effect_scatter <- function(model) {
  coef_table <- tidy(model) %>%
    filter(str_detect(term, "race") & !str_detect(term, "Multiracial")) %>%
    mutate(term=str_remove(term, "race")) %>%
    select(term, estimate, std.error) %>%
    bind_rows(tibble(term="White", estimate=0, std.error=NA)) %>%
    mutate(multiracial=str_detect(term, "/"))

  #calculate midway points
  temp <- coef_table %>%
    filter(!multiracial) %>%
    select(term, estimate)
  means <- apply(expand.grid(temp$estimate,temp$estimate), 1, mean)
  coef_table <- expand.grid(temp$term,temp$term) %>%
    mutate(term=paste(Var1, Var2, sep="/"),
           estimate_midpoint=means) %>%
    filter(Var1!=Var2) %>%
    select(term, estimate_midpoint) %>%
    right_join(coef_table) %>%
    mutate(estimate_midpoint=ifelse(is.na(estimate_midpoint), estimate,
                                    estimate_midpoint),
           estimate=ifelse(estimate==estimate_midpoint, 0, estimate))

  ggplot(coef_table, aes(x=estimate_midpoint, y=estimate_midpoint+estimate,
                         color=multiracial,
                         ymin=estimate_midpoint+estimate-1.96*std.error,
                         ymax=estimate_midpoint+estimate+1.96*std.error))+
    geom_abline(intercept = 0, slope=1, linetype=2, color="grey70")+
   # geom_hline(yintercept = 0, linetype=2, color="grey40")+
  #  geom_vline(xintercept = 0, linetype=2, color="grey40")+
    geom_linerange(alpha=0.5)+
    geom_point()+
    geom_text_repel(aes(label=term), min.segment.length = 0)+
    theme_bw()+
    scale_color_viridis_d(end=0.6)+
    labs(x="expected log odds ratio based on midway point",
         y="actual log odds ratio")
}
```

>>>>

```{r}
plot_effect_scatter <- function(model) {

  coefs <- tidy(model) %>%
    filter(str_detect(term, "race") & !str_detect(term, "Multiracial")) %>%
    mutate(term=str_remove(term, "race")) %>%
    select(term, estimate, std.error) %>%
    bind_rows(tibble(term="White", estimate=0, std.error=NA)) %>%
    mutate(multiracial=str_detect(term, "/"))

  #ok convert this to have single race groups for each multiracial group
  #panel and get the assumed midpoint value
  coef_table <- map(as.list(str_subset(coefs$term, "/")), function(x) {
    coefs %>%
      filter(term %in% c(x, str_split(x, "/")[[1]])) %>%
      mutate(mrace=factor(x,
                          levels=c("Black/White","White/Indigenous",
                                   "Black/Indigenous",
                                   "White/Latino","Black/Latino",
                                   "Indigenous/Latino",
                                   "White/Asian","Black/Asian",
                                   "Indigenous/Asian","Latino/Asian")),
             estimate_mid=ifelse(multiracial, 
                                 mean(estimate[!multiracial]),
                                 estimate),
             estimate=ifelse(multiracial, estimate_mid+estimate,
                             estimate))
  }) %>%
    bind_rows()

  ggplot(coef_table, aes(x=estimate_mid, y=estimate,
                         color=multiracial,
                         ymin=estimate-1.96*std.error,
                         ymax=estimate+1.96*std.error))+
    geom_abline(intercept = 0, slope=1, linetype=1, color="grey80")+
    geom_hline(data=subset(coef_table, !multiracial),
               aes(yintercept=estimate), linetype=3, color="grey80")+
    geom_linerange(alpha=0.5)+
    geom_point()+
    geom_text_repel(aes(label=term), size=3)+
    facet_wrap(~mrace, ncol=3)+
    theme_bw()+
    theme(legend.position = "none", panel.grid = element_blank())+
    scale_color_manual(values=c("grey40","black"))+
    labs(x="expected log odds ratio of grade retention based on midpoint",
         y="actual log odds ratio of grade retenion")
}
```

```{r}
temp <- plot_effect_scatter(model4)
```
